Reproducible and programmatic generation of neuroimaging visualisations

### 2022-03-17 manuscript.Rmd
.html/.docx added

---
title: "Reproducible and programmatic generation of neuroimaging visualisations"
author: "Sidhant Chopra & [coauthors]"
date: "09/03/2022"
output:
  pdf_document: default
  html_document: default
editor_options: 
  markdown: 
    wrap: 72
---

>>>>

---
title: "Reproducible and programmatic generation of neuroimaging visualisations"
author: "Sidhant Chopra & [coauthors]"
date: "09/03/2022"
output:
  html_document: default
  word_document: default
  pdf_document: default
editor_options:
  markdown:
    wrap: 72
---
